---
title: "Data Consolidation"
output: html_document
---

Goal: This step will consolidate all the web scrapred datafiles in prior step for sedans, hatchbacks, and SUVs into one csv file.

Installing Packages in R (Only if not previously installed). Using sqldf packages, which is a package that allows using Structured Query Language(SQL) in R. SQL is a lanaguage that allow to extract column and row data for a sturctured dataset (i.e. one with rows and columns)

```{r}
install.packages("sqldf")
```

Loading Necessary Libraries to R from above packages.

```{r}
library(sqldf)
```

Reading the datasets into a dataframe

```{r}
sedan = read.csv("sedan_data.csv", header = TRUE)
hatchback = read.csv("hatchback_data.csv", header = TRUE)
suv = read.csv("suv_data.csv", header = TRUE)

```

Running the below sql query to combine the above datafiles and create a column body_type to tell the difference of which file it came from

```{r}
unclean_truecar_data = sqldf("SELECT *, 'sedan' as body_type FROM sedan
                             union
                             SELECT *, 'hatchback' as body_type FROM hatchback
                             union
                             SELECT *, 'SUV' as body_type FROM suv")
```


Writing file obtained to a csv file.

```{r}

write.csv(unclean_truecar_data, "unclean_truecar_data.csv", row.names = FALSE)

```
