---
title: "Sentiment Data"
output: html_document
---

GOAL: Extract sentiment dataset from the website https://www.dealerrater.com/. Filters applied were Oklahoma City dealers and within a radius of 250 miles. Will extract headlines from reviews for sentiment analysis. 

Installing Packages in R (Only if not previously installed). Using rvest to get CSS selectors. Using dplyr to use pipe (if/then) functions.

```{r}
#install.packages("rvest")
#install.packages("dplyr")
```

Loading Necessary Libraries to R from above packages.

```{r}
library(rvest)
library(dplyr)
```

Creating an eempty dataframe to store captured data in tabular format

```{r}
sentiment_data = data.frame()
```


Scraping the first 11 pages (note: site as 12 pages) for ratings and reviews from site.

```{r}
for (pgnum in seq(from = 1, to = 11, by = 1)){
  link = paste0("https://www.dealerrater.com/directory/73127/Used-Car-Dealer/250/page",
                pgnum, "/?typedCriteria=73127&MinRating=1")
  page = read_html(link)
  
  rating = page %>% html_nodes(".rating-info") %>% html_text()
  review = page %>% html_nodes(".review-snippet") %>% html_text()
  
  sentiment_data = rbind(sentiment_data,data.frame(rating,review))
  
}
```

Writing data to a csv

```{r}
write.csv(sentiment_data, "dealer_review_data.csv", row.names = FALSE)
```

